### 2015-03-08 paper_10_intro.tex
use SDO everywhere instead of software development organization

    This work 
    provides a technique for a software development organization to create
    a single number score which indicates the overall performance
    of the organization. The
    score is based upon data collected for 5 key result indicators
    of a software development organization: quality, availability,
    satisfaction, schedule, and requirements.  It is not meant
    to be comparative between organizations, but to 
    form a historical baseline for a specific organization.  The single
    number is targeted for upper-level management whom need a quick
    and simple strategy to evaluate the performance of the organization.

@@

    Software development organizations are no different than 
    any other business or organization.  There are: tasks
    to be completed, goals to achieve (or miss), and measurements
    to be analyzed.  One difficulty with software development
    is the varied number and amount of measurements to be used. 
    It can be difficult to determine the correct activities
    to measure and the appropriate mechanism to report the measure.
    This has led organizations to either collect too little information
    or to collect too much information.  Another problem is the 
    inconsistency of the reported measures.  It is difficult to compare
    historical performance if the same measurements are not consistent
    throughout the recent history of an organization.

    Software development organizations need a framework to define
    what measurements should be tracked and how those measurements
    should be reported.  The Cumulative Result Indicator (CRI)
    framework provides a solid foundation
    for a consistent evaluation.  CRI analyzes the historical performance
    of a Software Development Organization (SDO)
    to create a baseline in order to provide a broad
    view of the overall organization.  It is common for software development
    organizations to measure and focus soley on the source code
    being produced.  However, a software development organization does more
    than just produce source code.  There is documentation to be
    written, testcases to be created, systems to be deployed, and
    decisions to be made.  The framework provides an evaluation
    of the overall software development organization, not just the
    source code.

@@

    Other attempts at evaluating a software development organization
    have been presented, but none produce a single number score for
    the entire effort of the software development organization. 
    The following are attempts to evaluate all or parts of 
    software development.

@@

    Although process mining can be useful for analyzing software
    development data, it has not yet been applied to the entirety 
    of a software development organization. It also does not
    focus on the results of the organization.  It focuses
    on process conformance, which can be very important, so it
    is limited in the ability to evaluate the entire organization.

    Much work has been done to determine metrics for source code, in fact 
    entire books have been written on the topic of software 
    metrics \cite{Jones1996, Putnam2013}. Yet, 
    organizations still struggle to measure the production of software.
    Little work exists
    for scoring the entire software development organization.

@@

    Another measurement of quality can be the cost per defect, also 
    known as the cost to fix a problem.  As seen in \cite{Jones2013},
    this measurement has problems because the lowest cost per
    defect will occur on software with the most problems.  Therefore,
    the lowest cost per defect is actually the lowest quality as well.
    Due to this difficulty and others, a number of other models
    have been created for evaluating the quality of software 
    \cite{Miguel2014}.  While all of the models have merit
    in certain situations, the measures of quality must be combined
    with other measures in order to provide an overall evaluation
    of a software development organization.

@@

    One area of research that is focusing on the evaluation 
    of software development organizations
    is \textit{software analytics}. 
    Software analytics is less focused on evaluation
    and more so on all sorts of analysis of software data.
    The earliest variants
    of software analytics were disguised as
    applications of data mining techniques to software 
    engineering data in the 
    late 1990s \cite{Ruhe1997,Ebert1999,Goel1997}.   
    Later the field began to emerge more heavily, but still
    remained primarily methods of data mining applied to 
    software engineering \cite{Kaner2004,Xie2009,Taylor2010,Halkidi2011}. 
    Finally, The term software intelligence was proposed for the field of study
    \cite{Hassan2010}, but eventually
    the term software analytics became the dominant term for referring to the 
    field of study \cite{Buse2010, Zhang2011}.

@@

    The remainder of this dissertation is divided into 7 chapters.  Chapter 2 provides
    an overview of software, software development life cycles, software engineering, and software
    development organizations.  Chapter 3 introduces some existing techniques for measuring
    a software development organization. Chapter 4 then provides an explanation of the Cumulative
    Result Indicator (CRI).  It will present the essential elements for calculating the CRI, as well
    as the formulas, framework, and data necessary to produce the CRI. Chapter 5 provides
    a technological framework for storing the current and historical CRI values.
    Chapter 6 demostrates how CRI can be implemented in a software development portion of 
    a large financial institution. Chapter 7 discusses some possible future directions 
    for further enhancements. Chapter 8 concludes the dissertation with a summary
    of the results.

>>>>

    This work 
    provides a technique for a Software Development Organization (SDO) to create
    a single number score which indicates the overall performance
    of the organization. The
    score is based upon data collected for 5 key result indicators
    of an SDO: quality, availability,
    satisfaction, schedule, and requirements.  It is not meant
    to be comparative between organizations, but to 
    form a historical baseline for a specific organization.  The single
    number is targeted for upper-level management whom need a quick
    and simple strategy to evaluate the performance of the organization.

@@

    An SDO is no different than 
    any other business or organization.  There are: tasks
    to be completed, goals to achieve (or miss), and measurements
    to be analyzed.  One difficulty with software development
    is the varied number and amount of measurements to be used. 
    It can be difficult to determine the correct activities
    to measure and the appropriate mechanism to report the measure.
    This has led organizations to either collect too little information
    or to collect too much information.  Another problem is the 
    inconsistency of the reported measures.  It is difficult to compare
    historical performance if the same measurements are not consistent
    throughout the recent history of an organization.

    SDOs need a framework to define
    what measurements should be tracked and how those measurements
    should be reported.  The Cumulative Result Indicator (CRI)
    framework provides a solid foundation
    for a consistent evaluation.  CRI analyzes the historical performance
    of an SDO
    to create a baseline in order to provide a broad
    view of the overall organization.  It is common for software development
    organizations to measure and focus soley on the source code
    being produced.  However, an SDO does more
    than just produce source code.  There is documentation to be
    written, testcases to be created, systems to be deployed, and
    decisions to be made.  The framework provides an evaluation
    of the overall SDO, not just the
    source code.

@@

    Other attempts at evaluating an SDO
    have been presented, but none produce a single number score for
    the entire effort of the SDO. 
    The following are attempts to evaluate all or parts of 
    software development.

@@

    Although process mining can be useful for analyzing software
    development data, it has not yet been applied to the entirety 
    of an SDO. It also does not
    focus on the results of the organization.  It focuses
    on process conformance, which can be very important, so it
    is limited in the ability to evaluate the entire organization.

    Much work has been done to determine metrics for source code, in fact 
    entire books have been written on the topic of software 
    metrics \cite{Jones1996, Putnam2013}. Yet, 
    organizations still struggle to measure the production of software.
    Little work exists
    for scoring the entire SDO.

@@

    Another measurement of quality can be the cost per defect, also 
    known as the cost to fix a problem.  As seen in \cite{Jones2013},
    this measurement has problems because the lowest cost per
    defect will occur on software with the most problems.  Therefore,
    the lowest cost per defect is actually the lowest quality as well.
    Due to this difficulty and others, a number of other models
    have been created for evaluating the quality of software 
    \cite{Miguel2014}.  While all of the models have merit
    in certain situations, the measures of quality must be combined
    with other measures in order to provide an overall evaluation
    of an SDO.

@@

    One area of research that is focusing on the evaluation 
    of SDOs
    is \textit{software analytics}. 
    Software analytics is less focused on evaluation
    and more so on all sorts of analysis of software data.
    The earliest variants
    of software analytics were disguised as
    applications of data mining techniques to software 
    engineering data in the 
    late 1990s \cite{Ruhe1997,Ebert1999,Goel1997}.   
    Later the field began to emerge more heavily, but still
    remained primarily methods of data mining applied to 
    software engineering \cite{Kaner2004,Xie2009,Taylor2010,Halkidi2011}. 
    Finally, The term software intelligence was proposed for the field of study
    \cite{Hassan2010}, but eventually
    the term software analytics became the dominant term for referring to the 
    field of study \cite{Buse2010, Zhang2011}.

@@

    The remainder of this dissertation is divided into 7 chapters.  Chapter 2 provides
    an overview of software, software development life cycles, software engineering, and software
    development organizations.  Chapter 3 introduces some existing techniques for measuring
    an SDO. Chapter 4 then provides an explanation of the Cumulative
    Result Indicator (CRI).  It will present the essential elements for calculating the CRI, as well
    as the formulas, framework, and data necessary to produce the CRI. Chapter 5 provides
    a technological framework for storing the current and historical CRI values.
    Chapter 6 demostrates how CRI can be implemented in a software development portion of 
    a large financial institution. Chapter 7 discusses some possible future directions 
    for further enhancements. Chapter 8 concludes the dissertation with a summary
    of the results.

### 2015-03-08 paper_20_sdo.tex
work on chapter 5, SDLC-AE
use SDO everywhere instead of software development organization

\section{A SOFTWARE DEVELOPMENT ORGANIZATION (SDO)}
A \textit{Software Development Organization (SDO)} is any organization or subset of an organization that is responsible
for the creation, deployment, and maintenance of software.  Many times a software development organization
is a company that produces software.  Other times, a software development organization is contained
within the Information Technology department of a larger organization. Some of the job roles
with an SDO are: software engineer, system administrator, software quality analyst,
programmer, database administrator, and documentation specialist.

@@

\subsection{WHAT IS SOFTWARE ENGINEERING?}
    \textit{Software Engineering} as a term dates back to the 
    1968 North Atlantic Treaty Organization (NATO) conference \cite{Tsui2013, Naur1969}. Over the 
    years many definitions have been provided.  IEEE provides a definition that encompasses many of the
    other definitions.  IEEE ISO610.12 defines software engineering as, 
    ''The application of a systematic, disciplined, quantifiable approach to the development, operation, and maintenance of software''
    \cite{Ieee1990}.

>>>>

\section{A SOFTWARE DEVELOPMENT ORGANIZATION (SDO)}
A \textit{Software Development Organization (SDO)} is any organization or subset of an organization that is responsible
for the creation, deployment, and maintenance of software.  Many times an SDO
is a company that produces software.  Other times, an SDO is contained
within the Information Technology department of a larger organization. Some of the job roles
with an SDO are: software engineer, system administrator, software quality analyst,
programmer, database administrator, and documentation specialist.

@@

\subsection{WHAT IS SOFTWARE ENGINEERING?}
\label{sec:swe}
    \textit{Software Engineering} as a term dates back to the 
    1968 North Atlantic Treaty Organization (NATO) conference \cite{Tsui2013, Naur1969}. Over the 
    years many definitions have been provided.  IEEE provides a definition that encompasses many of the
    other definitions.  IEEE ISO610.12 defines software engineering as, 
    ''The application of a systematic, disciplined, quantifiable approach to the development, operation, and maintenance of software''
    \cite{Ieee1990}.

### 2015-03-08 paper_40_cri.tex
use SDO everywhere instead of software development organization

    Software development organizations struggle to measure overall performance.  
    The \textit{Cumulative Result Indicator (CRI)} is an algorithm to provide a single 
    number score to measure the performance of a software development organization. 
    It works by statistically analyzing the past performance of the 
    organization and using that information to score an organization 
    on current performance.  CRI is a collection of the following 5 
    elements, which are actually KRIs,
    for a software development organization.
    \textbf{
    \begin{enumerate}
        \item Quality
        \item Availability
        \item Satisfaction
        \item Schedule
        \item Requirements
    \end{enumerate}
    }
    A separate CRI
    score is calculated for each element and 
    then aggregated together to form an overall 
    CRI score.  A new CRI score will be calculated based
    upon the selection of a given time period (weekly, monthly, quarterly).
    \textbf{CRI is not meant to be comparative between
    organizations, but to measure the amount of increase or decrease
    a single organization exhibits across elements}.  CRI is made to be easily 
    expandable to other elements if desired.

@@

        \subsubsection{CRI VS. FOCUS AREAS OF SOFTWARE ANALYTICS}
            Also, section \ref{subsub:softwareanalytics} mentions 3 important questions that
            software analytics must address.  Table \ref{tab:questions} presents the 3 questions
            and a description of how CRI addresses that specific question.  It is clear
            that CRI addresses the questions.  CRI is a beneficial technique of software
            analytics when applied to software development organizations.

@@

                How much better is my model performing than a naive strategy, such as guessing? & CRI 
                provides consistency which may not exist without it.  Therefore, CRI removes the 
                guesswork of measuring a software development organization. \\
                \myrowcolour%
                How practically significant are the results? & The CRI score is consistent
                and easy to comprehend.  Thus comparison with past performance is quick 
                and simple.  This is a significant advantage for software 
                development organizations. \\
                How sensitive are the results to small changes in one or more of the inputs? & 
                The question was extensively addressed in section \ref{sec:sensitivity}.  It appears CRI is
                not overly sensitive to small changes in the inputs.\\

>>>>

    SDOs struggle to measure overall performance.  
    The \textit{Cumulative Result Indicator (CRI)} is an algorithm to provide a single 
    number score to measure the performance of an SDO. 
    It works by statistically analyzing the past performance of the 
    organization and using that information to score an organization 
    on current performance.  CRI is a collection of the following 5 
    elements, which are actually KRIs,
    for an SDO.
    \textbf{
    \begin{enumerate}
        \item Quality
        \item Availability
        \item Satisfaction
        \item Schedule
        \item Requirements
    \end{enumerate}
    }
    A separate CRI
    score is calculated for each element and 
    then aggregated together to form an overall 
    CRI score.  A new CRI score will be calculated based
    upon the selection of a given time period (weekly, monthly, quarterly).
    \textbf{CRI is not meant to be comparative between
    organizations, but to measure the amount of increase or decrease
    a single organization exhibits across elements}.  CRI is made to be easily 
    expandable to other elements if desired.

@@

        \subsubsection{CRI VS. FOCUS AREAS OF SOFTWARE ANALYTICS}
            Also, section \ref{subsub:softwareanalytics} mentions 3 important questions that
            software analytics must address.  Table \ref{tab:questions} presents the 3 questions
            and a description of how CRI addresses that specific question.  It is clear
            that CRI addresses the questions.  CRI is a beneficial technique of software
            analytics when applied to SDOs.

@@

                How much better is my model performing than a naive strategy, such as guessing? & CRI 
                provides consistency which may not exist without it.  Therefore, CRI removes the 
                guesswork of measuring an SDO. \\
                \myrowcolour%
                How practically significant are the results? & The CRI score is consistent
                and easy to comprehend.  Thus comparison with past performance is quick 
                and simple.  This is a significant advantage for software 
                development organizations. \\
                How sensitive are the results to small changes in one or more of the inputs? & 
                The question was extensively addressed in section \ref{sec:sensitivity}.  It appears CRI is
                not overly sensitive to small changes in the inputs.\\
